---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# madlibs

<!-- badges: start -->
<!-- badges: end -->


The goal of madlibs is to be able to replace words in prose with incomplete versions of the words.  

## Installation

You can install the development version of madlibs from github.com with:

``` r
devtools::install_github("EvaMaeRey/madlibs")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(madlibs)
madlibs::remove_aeiou(x = "Hello, World!")
```

You will probably want to use the function [inline](https://rmarkdown.rstudio.com/lesson-4.html), in the middle of a paragraph so you get a result like this to gently test some knowledge:

*People can makes sense of relationships in data when it is v \_ s \_ \_ l \_ z \_ d much more easily than when it is in its raw, table form. The package ggplot2 is a package implementing the gr \_ mm \_ r of gr \_ ph \_ cs; the underlying philosophy is also used in Tableau and D3 (a java script library).*


```{r, eval = T}
set.seed(1234)
drop_words(x = "The woods are lovely, dark and deep", frac = .3)
```

---

```{r, eval = F}
create_wandered_lonely() %>% 
  drop_words(frac = .1)
```

