---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# madlibs

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->


The goal of madlibs is to be able to replace words in prose with incomplete versions of the words or drop words altogether.

## Installation

You can install the development version of madlibs from github.com with:

``` r
devtools::install_github("EvaMaeRey/madlibs")
```

## Drop vowels


```{r, results='asis'}
library(magrittr)
library(madlibs)
drop_vowels(x = "Hello, World!")
```

You will probably want to use the function [inline](https://rmarkdown.rstudio.com/lesson-4.html), in the middle of a paragraph so you get a result like this to gently test some knowledge:

*People can makes sense of r drop_vowels("relationships")` in data when it is v \_ s \_ \_ l \_ z \_ d much more easily than when it is in its raw, table form. The package ggplot2 is a package implementing the gr \_ mm \_ r of gr \_ ph \_ cs; the underlying philosophy is also used in Tableau and D3 (a java script library).*

# Drop words

```{r, eval = T, results='asis'}
drop_words(x = "The woods are lovely, dark and deep", frac = .5)
```

---

```{r, eval = T, results='asis'}
madlibs:::create_wandered_lonely() %>% 
  drop_words(frac = .3) 
```

